On The Difficulty of Computing Non-Commutative Signature Gröbner Bases

### 2022-07-13 article_issac.tex
Petite erreur de calcul corrigée dans la partie 7 + quelques détails ajoutées à la preuve dans cette partie.

We then have the following fact:
\begin{itemize}
\item $s_1=\underline{xy \varepsilon_2}+\varepsilon_2 y^2+ x \varepsilon_1 y^2+y \varepsilon_1 y^2+ \varepsilon_1 x y^2 \in Syz(f_1,f_2)$,
\item $s_2=\underline{xy \varepsilon_1}-yx\varepsilon_1 -  \varepsilon_1 x^2+y \varepsilon_1 xy \in Syz(f_1,f_2)$.
\end{itemize}
In addition, the following are trivial syzygys:

@@

We then state that:
\begin{lem}
The module of syzygys $Syz(f_1,f_2)$ admits $(s_1,\dots,s_6)$
as a Gröbner basis.
\end{lem}
\begin{proof}
Let $m=a \varepsilon_1 b \in \MM \left( \mathscr{F}_2 \right)$
be a leading monomial of a syzygy $s$.
Then we distinguish the following cases.
\begin{enumerate}
\item If $a = \dots x$ then $m$ is divisible by $\LM(s_3).$
\item If $a = \dots xy$ then $m$ is divisible by $\LM(s_2).$
\item If $a = \dots y^2$ then $m$ is divisible by $\LM(s_4).$
\item If $a = y,$ then $s = y \varepsilon_1 u+  \varepsilon_1 v + \varepsilon_2 w$ for some polynomials $u,v,w.$
Applying $\overline{\cdot}$ (mapping $\varepsilon_i$ to $f_i$), we 
obtain that $u=v=w=0$ which is a contradiction.
\item If $a = 1,$ then $s = \varepsilon_1 u+  \varepsilon_2 v $ for some polynomials $u,v.$
Again, applying $\overline{\cdot}$, we 
obtain that $u=v=0$ which is a contradiction.
\end{enumerate}
Similarly, let $m=a \varepsilon_2 b \in \MM \left( \mathscr{F}_2 \right)$
be a leading monomial of a syzygy $s$. Then:
\begin{enumerate}
\item If $a = \dots x$ then $m$ is divisible by $\LM(s_5).$
\item If $a = \dots xy$ then $m$ is divisible by $\LM(s_1).$
\item If $a = \dots y^2$ then $m$ is divisible by $\LM(s_6).$
\item If $a = y,$ we obtain a contradiction.
\item If $a = 1,$ we also obtain a contradiction.
\end{enumerate}

>>>>

We then have the following fact:
\begin{itemize}
\item $s_1=\underline{xy \varepsilon_2}-\varepsilon_2 y^2+ x \varepsilon_1 y^2-y \varepsilon_1 y^2- \varepsilon_1 x y^2 \in Syz(f_1,f_2)$,
\item $s_2=\underline{xy \varepsilon_1}-yx\varepsilon_1 -  \varepsilon_1 x^2+y \varepsilon_1 xy \in Syz(f_1,f_2)$.
\end{itemize}
In addition, the following are trivial syzygys:

@@

We then state that:
\begin{lem}
The module of syzygys $Syz(f_1,f_2)$ admits $(s_1,\dots,s_6)$
as a Gröbner basis.
\end{lem}
\begin{proof}
Let $m=a \varepsilon_1 b \in \MM \left( \mathscr{F}_2 \right)$
be a leading monomial of a syzygy $s$.
Then we distinguish the following cases.
\begin{enumerate}
\item If $a = \dots x$ then $m$ is divisible by $\LM(s_3).$
\item If $a = \dots xy$ then $m$ is divisible by $\LM(s_2).$
\item If $a = \dots y^2$ then $m$ is divisible by $\LM(s_4).$
\item If $a = y,$ then $s = y \varepsilon_1 u+  \varepsilon_1 v + \varepsilon_2 w$ for some polynomials $u,v,w.$
Applying $\overline{\cdot}$ (mapping $\varepsilon_i$ to $f_i$), we 
obtain that $y (x-y) u+  (x-y) v + y^2 w=0.$
On the left hand-side, the polynomial $xv$ contains all the monomials
with prefix $x$, which implies 
that no cancellation with other terms can occur,
and then $v=0.$
Similarly, $yxu$ contains all the monomials
with prefix $yx$, which then implies that
$u=0$ and then $y^2 w=0$ and $w=0$, and we get
a contradiction.
\item If $a = 1,$ then $s = \varepsilon_1 u+  \varepsilon_2 v $ for some polynomials $u,v.$
Again, applying $\overline{\cdot}$, we 
obtain that $u=v=0$ which is a contradiction.
\end{enumerate}
Similarly, let $m=a \varepsilon_2 b \in \MM \left( \mathscr{F}_2 \right)$
be a leading monomial of a syzygy $s$. Then:
\begin{enumerate}
\item If $a = \dots x$ then $m$ is divisible by $\LM(s_5).$
\item If $a = \dots xy$ then $m$ is divisible by $\LM(s_1).$
\item If $a = \dots y^2$ then $m$ is divisible by $\LM(s_6).$
\item If $a = y,$ we obtain a contradiction.
\item If $a = 1,$ we also obtain a contradiction.
\end{enumerate}
